### 2014-02-21 paper/retrofit.tex
minor

\begin{mathpar}
\and
\inferrule[T-pure]
{| te ~> te'|}
{| conf tS te -> conf tS te' |}

\and
\inferrule[T-app]
{ } {| intE ((\x.te) tv) ~> intE ({tv/x} tv) |}

\and
\inferrule[T-ifTrue]
{ } {| intE (if true then te1 else te2)  ~> intE te1 |}

\and
\inferrule[T-ifFalse]
{ } {| intE (if false then te1 else te2) ~> intE te2 |}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
io   ::=  (il, id ie)
Q    ::=  nil | io :: Q

@@

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
.->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 :: cdots :: iok :: (il', id', ie')|\\
| iS' = iS[id mapsto io1 :: cdots :: iok]|\\
| ie1'' = {ie'/ix1,id'/ix2} ie1|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
.->
iconf iS' (lconf id il tS (iniE ie1''), ldots)
|}

@@

\inferrule[I-pure]
{| ie .~> ie'|}
{|
  iconf iS (lconf id il tS ie)
.->
  iconf iS (lconf id il tS ie)
|}

\and
\inferrule[I-labelOp]
{ |denot (il lop il') = iv|}
{ |iniE (il lop il') .~> iniE iv| }

\and
\inferrule[I-border]
{ } {| iniE (IT (TI (ie))) .~> iniE ie |}

@@

The filter function |filter il Q| removes message whose labels do not
flow to |il|. Specifically, if |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|; otherwise:
\[
|filter il ((il', id, ie) :: Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) :: filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]

>>>>

\begin{mathpar}
\and
\inferrule[T-pure]
{| te ~> te'|}
{| conf tS (iniE te) -> conf tS (iniE te') |}

\and
\inferrule[T-app]
{ } {| (\x.te) tv ~> {tv/x} te |}

\and
\inferrule[T-ifTrue]
{ } {| if true then te1 else te2  ~> te1|}

\and
\inferrule[T-ifFalse]
{ } {| if false then te1 else te2  ~> te2|}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
io   ::=  (il, id ie)
Q    ::=  nil | io , Q

@@

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
.->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
| ie1'' = {ie'/ix1,id'/ix2} ie1|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
.->
iconf iS' (lconf id il tS (iniE ie1''), ldots)
|}

@@

\inferrule[I-pure]
{| ie .~> ie'|}
{|
  iconf iS (lconf id il tS (iniE ie))
.->
iconf iS (lconf id il tS (iniE ie))
|}

\and
\inferrule[I-labelOp]
{ |denot (il lop il') = iv|}
{ |il lop il' .~> iv| }

\and
\inferrule[I-border]
{ } {| IT (TI (ie)) .~> ie |}

@@

The filter function |filter il Q| removes message whose labels do not
flow to |il|. Specifically, if |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|; otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
